Finding Bugs in JavaScript Engines with Differential Testing---an Experience Report

### 2018-06-04 paper/paper.tex
paper sketch

\documentclass[11pt]{article}
%\documentclass[dvips,11pt]{article}

% \usepackage{natbib}
% \setlength{\bibsep}{0pt plus 0.3ex}
\usepackage[margin=1cm]{caption}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
%,nohead,nofoot
%\usepackage[margin=1n,left=1cm,top=1cm,right=1.75cm,bottom=1.5cm]{geometry}
\usepackage[margin=1in,includeheadfoot,left=1cm,top=0.5cm,right=1.5cm,bottom=0.5cm]{geometry}
%\usepackage[margin=1in,includeheadfoot]{geometry}
\usepackage{url}
\usepackage{cite}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{subfigure}
% ADD THE FOLLOWING COUPLE LINES INTO YOUR PREAMBLE
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.3ex}
}

\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{darkaquamarine}{rgb}{0.2,0.4,0.3}
%% macros
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
\newcommand{\Mar}[1]{\textbf{[[Marcelo:~}{\color{blue} #1}\textbf{]]}}
\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
\newcommand{\Igor}[1]{\textbf{[[}{\color{darkaquamarine} #1}\textbf{]]}}
\newcommand{\Comment}[1]{}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}

%% \setlength{\oddsidemargin}{0.25in}
%% \setlength{\textwidth}{6.5in}
%% \setlength{\topmargin}{0in}
%% \setlength{\textheight}{8.5in}

%\renewcommand\Affilfont{\fontsize{9}{10.8}\itshape}
% These force using more of the margins that is the default style

@@

\title{Finding Bugs in JavaScript Engines with Differential Testing}
\author{}
\date{}

% You can leave out "date" and it will be added automatically for today
% You can change the "\today" date to any text you like

\makeatletter
\def\maketitle{%
  \par{\centering\large\textbf{\@title}\normalsize\par}\vspace{3ex}%
  \par{\@author}%
  \par}
\makeatother

@@

\vspace{-2ex}
\small    
\begin{table}[h!] 
  \centering%% Centro de Inform\'atica - CIn \\
  \begin{tabular*}{.85\linewidth}{l}

    Marcelo d'Amorim and Igor Sim\~oes (M.Sc. student)\\

    Postal Address: Av. Jornalista Anibal Fernandes, S/N. Cidade
    Universit\'aria, PE, Brazil, 50.740-560 \\

    Email addresses: \{damorim, isol2\}@cin.ufpe.br\\

    Phones: +55 (81) 2126-8430,
    ext. 4379 [work], +55 (81) 98800-2010 [mobile]\\

    Affiliation: Federal University of Pernambuco, Department of
    Computer Science\\

    Contacts:~Martin Barbella (mbarbella@google.com), Vilas Jagannath (vilasshekharbj@gmail.com)

  \end{tabular*}
\end{table}
\normalsize

\vspace{-2ex}
\begin{abstract}
JavaScript (JS) is a fundamental programming language for the
web. Finding bugs in JavaScript engines is an important problem. This
proposal describes our differential testing infrastructure for testing
JS engines, our current results, and upcoming features to improve
bug-finding in JS engines.
\end{abstract}

\section{Problem Space}

%% Its niche is front-end and
%% back-end web development\Comment{, supported several frameworks and
%%   runtimes (\eg{}, Express.js and Node.js)}.

%% In fact, bugs in JS implementations are often reported by
%% the general public, some of which were reported by our team.
%% (confirmed by engine developers; see
%% Section~\ref{sec:results}) using a prototype of our solution (see
%% Section~\ref{sec:design}).

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
demands of the community. These changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions. Automated test generation can help reduce the
cost of testing, but the lack of executable specifications is an
important obstacle. In particular, it is an obstacle to find functional errors.

%\vspace{-1ex}
\begin{center}
\fbox{
  \begin{minipage}{13.5cm}
    \centering \textit{The goal of this project is to find bugs in
      implementations of JavaScript engines by leveraging diversity
      across implementations.}
  \end{minipage}
}
\end{center}
%\vspace{-1ex}

Differential testing\cite{McKeeman98differentialtesting} has been
applied in a variety of
contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
to mitigate the oracle problem,
but it has not been thoroughly explored to find functional bugs in JS
engines. The closest work was done by Patra and
Pradel~\cite{patra2016learning}, where they evaluated their proposed
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. This project aims at building and evaluating an
infrastructure for differential testing of runtime engines, such as
the JS engine or WebAssembly's. The sensible parts of the
infrastructure are the checks of input validity (as to reduce
waste/cost) and output correctness (as to reduce false positives).

\section{Design Space}
\label{sec:design}

\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
  \vspace{-5ex}
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
  \vspace{-5ex}  
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs~\cite{fuzz-testing-history} with the typical goal of
finding crashes. Several fuzzing methods have been proposed in the
past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}). Figure~\ref{fig:workflow} shows a generic pipeline of a
fuzzer infrastructure, instantiated to our problem. Arrows indicate data flow; lines
with no arrow denote encapsulation. In our case, JS files are
provided as seeds to bootstrap the process. These files can
originate from the test suites of the engine codebases or from the bug
reports in their issue trackers. The fuzzing infrastructure selects
randomly one of the inputs to fuzz with a given tool, say the
black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
infrastructure can discard syntactically invalid
inputs using an external parser for the input language; semantically
invalid inputs can be prevented with with linters. Once the input is
found to be likely valid, the infrastructure
invokes the oracle to check correctness. In case all engines
consider the test output consistent (\ie{}, all pass or all fail), the
infrastructure discards the corresponding input. Otherwise, it considers that
input as potentially fault-revealing and interesting. Currently, we
classify alarms in the HI and LO groups. The HI group includes
those warnings that manifest execution errors spawned directly by the
test (or its close neighborhood) whereas the LO group includes the
rest of the warnings. \Igor{We found empirically that 88\% of the
issues reported are included in the HI group and 58\% of them was confirmed}.

@@

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{t}[0pt]{0.5\textwidth}
  \vspace{-3ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{wraptable}

@@

The workflow described in Section~\ref{sec:design} is currently
functional. This section shows preliminary results obtained with our
infrastructure providing some evidence that finding bugs in JS runtime
engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42 days. For example, bug \# 6 was manifested by the JS code \CodeIn{var
  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
function that returns a primitive value identifying the target
object~\cite{valueof}. That function returns an empty string in the
original version of this code. The modified version of the code
returns a string representation of a null character (called
\CodeIn{NUL} in ascii).
\Igor{The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
is equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
that converts a string to a number, otherwise the operation returns NaN 
(Not a Number)\cite{unary-plus}}. For this case, \Igor{isto esta correto? $\rightarrow$ all engines but} Chakra evaluate the unary
plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.

So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any new bug on SpiderMonkey and V8; the bugs we
found were duplicates and were not reported. Finally, it is
worth noting that \Igor{7 out of 17} JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

%% \Igor{
%%   Nowadays, we used six javascript engines suites with approximately 2K of javascript files 
%%   that could be fuzzed. Currently, using our infrastructure we reported \Fix{13}
%%   bugs so far. The Table~\ref{tab:bugs} exposes all bugs found and reported by our team.
%%   At this moment, the status are: \Fix{6} issues was tagged as new, \Fix{4} was confirmed
%%   and \Fix{2} of them was merged and closed. Unfortunally, \Fix{1} of them was rejected
%%   due the engine does not follows the specification and dozens of others warnings already been
%%   reported previously.

%%   The Figure~\ref{fig:bug-chakra} exposes a fuzzed file generated by radamsa in our environment, it was observed
%%   that the fuzzer replace the empty string at Line 3 and replace it with the hexadecimal value "\textbackslash x00".
%%   The bug manifests in Line 7, according to ES6 specification on Mozilla dev website
%%   \footnote{Unary Plus \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/Arithmetic_Operators}},
%%   the unary plus converts the variable to an integer if it is a valid value
%%   otherwise returns NaN. The Figure~\ref{fig:pattern} shows the log output from our infrastructure,
%%   see that we set automatically this testcase as high priority because it is a failure by assertion.
%%   The differential test across all engines, shows a unexpected behaviour of ChakraCore engine that passes in this test case.
%%   It was necessary a manual inspection to check if it is a real bug, we observed that 
%%   ChakraCore indentify "\textbackslash x00" as a null terminator instead of invalid parser object making
%%   the unary plus converts null to 0.
%% }
%% \Fix{nao estou conseguindo mesclar dois listings com subfigure, por favor alguem tenta fazer isso por mim.}
%% \Igor{Coloco outro caso de bug reportado?}

%\input{bugs}
%\input{bug_table}

\section{Future Steps}

The list below shows future tasks for this project.

\begin{itemize}
\item Integrate different fuzzers, including AFL~\cite{afl},
  HonggFuzz~\cite{honggfuzz}, LibFuzzer~\cite{libfuzzer}, jsfunfuzz~\cite{jsfunfuzz}, and
  Grammarinator~\cite{grammarinator}.

\item Find balance between generational strategies (, which often
  produce valid but simple inputs) and mutational strategies (, which
  often produce complex but invalid inputs) for fuzzing.

\item Explore different strategies to reduce the number of false
  positives as to facilitate the inspection process. For example,
  mining issue trackers for similar bug reports is a candidate alternative.

\item Look for bugs in WebAssembly~\cite{webassembly}, a new binary format already
  supported by major browsers. In principle, our infrastructure is
  agnostic to the runtime engine used. We are eager to explore other
  sources of bugs, especially in very new engines.

\end{itemize}

%% \MAB{Unfortunately the low-hanging fruit for this project was already
%%   picked \cite{patra2016learning}, so I believe you should focus on
%%   taming implementation-specific behavior and/or the testing
%%   infrastructure (i.e. how to organize all those fuzzers and make them
%%   work together). You might also want to mention the possibility of
%%   fuzzing
%%   \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{WebAssembly}
%%   directly: LLVM already has (some) support for targeting WebAssembly,
%%   which means that we'll be able to run, in the near future, pretty
%%   much every language with an LLVM-backed compiler in a browser.}

\section{Data Policy}

The results produced with this research will be made available to the
public and to the research community.  All tools and data sets
developed will be available online, and the software will be released
under an open source license.

\footnotesize
\bibliographystyle{plain}
\bibliography{tmp}

@@

%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL NUL
%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly ascii
%%  LocalWords:  valueOf unary NaN Chakra cccccc Url JavascriptCore
%%  LocalWords:  cgi tmp

>>>>

%\documentclass[conference]{IEEEtran}
\documentclass[10pt,conference,anonymous]{IEEEtran}
\IEEEoverridecommandlockouts

\input{packages}
\input{macros}

@@

\title{Finding Bugs in JavaScript Engines with Differential
  Testing---an Experience Report}

%% \author{
%% \IEEEauthorblockN{Sabrina Souto}
%% \IEEEauthorblockA{State University of Para\'iba\\
%% Para\'iba, Brazil\\
%% sabrinadfs@gmail.com}
%% \and
%% \IEEEauthorblockN{Marcelo d'Amorim}
%% \IEEEauthorblockA{Federal University of Pernambuco\\
%%   Pernambuco, Brazil\\
%%   damorim@cin.ufpe.br}
%% \and
%% \IEEEauthorblockN{Rohit Gheyi}
%% \IEEEauthorblockA{Federal University of Campina Grande\\
%%   Para\'iba, Brazil\\
%%   rohit@dsc.ufcg.edu.br}
%% }

@@

\begin{abstract}
\end{abstract}

\begin{IEEEkeywords}
...
\end{IEEEkeywords}

\section{Introduction}

JavaScript (\js{}) is one of the most popular programming languages of
today~\cite{business-insider,stackify}. The \js{} specification
changes relatively frequently to accommodate the pressing demands of
the community. For example, the JS specification went through a severe
change recently called by the name of ECMAScript6
(ES6)~\cite{es6-features}.  These changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions. Automated techniques can help finding
bugs, but the lack of executable specifications limits their ability
to detect errors not manifested by universal oracles.

This paper reports on a study to find those kinds of bugs in
JavaScript engines. The goal of the study is to improve quality of
existing \js{} engines by improving the bug finding process. We used
differential testing~\cite{Brumley-etal-ss07}, a technique that has
been applied in a variety of
contexts~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
to address the oracle problem. Differential testing leverages the
diversity across system's implementations to detect anomalous
behavior. \Mar{this needs work$\rightarrow$}
\Fix{but it has not been thoroughly explored to find functional bugs in JS
engines. The closest work was done by Patra and
Pradel~\cite{patra2016learning}, where they evaluated their proposed
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. This project aims at building and evaluating an
infrastructure for differential testing of runtime engines, such as
the JS engine or WebAssembly's. The sensible parts of the
infrastructure are the checks of input validity (as to reduce
waste/cost) and output correctness (as to reduce false positives).}

\section{Infrastructure}
\label{sec:design}

%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
\begin{figure}[h]
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \caption{\label{fig:workflow}Infrastructure.}
\end{figure}

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Arrowed lines indicate control
flow (dashed) and data flow (filled); lines with no arrow denote
encapsulation. The bug-finding process takes on input JS files
originating from the regression test suites of various JS engines. It
is worth noting that we found online regression suites for a total of
\Fix{YY} JS engines.\Mar{show table with name and count of JS files}
If input fuzzing~\cite{fuzz-testing-history} is not selected, the
oracle checks whether or not the output is consistent across all
engine implementations. In case the test passes in all engines or
fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the corresponding input. Otherwise, it
considers the input as potentially fault-revealing; hence interesting
for human inspection. If fuzzing is selected, new inputs are obtained
from a given input using some off-the-shelf fuzzer; the workflow is
similar to that of no fuzzing. Several fuzzing methods have been
proposed in the past, varying with respect to how new inputs are
generated (\eg{}, coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}). \Mar{which ones we covered? why is this
  relevant?}

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. The HI
group includes those inputs that manifest anomaly directly by the test
(or its close neighborhood) as opposed to anomaly in some JS
function. The rationale is that the test was able to execute to
completion without violating any internal checks of the API, but
failed to satisfy some check of the test. The LO group, in contrast,
includes those cases where the anomaly was observed executing some JS
function. We found that engine implementations often check
pre-conditions of API functions differently, leading to premature
failures. Most of the inputs in this category failed to satisfy the
pre-condition check of some, but not all engines. Although we did find
real bugs from warnings manifested in this category, the proportion is
much lower compared to the HI category--only 12\% of the reals bugs we
found originated from the LO category.\Mar{can we detect dups mining
  issue trackers?}

\Mar{show real examples of HI and LO and provide the
  rationale for such classification.}

%% selects randomly one of the inputs to fuzz with a
%% given tool, say the black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration produces a new
%% file. For grammar-agnostic fuzzers, like Radamsa, the infrastructure
%% can discard syntactically invalid inputs using an external parser for
%% the input language; semantically invalid inputs can be prevented with
%% with linters. Once the input is found to be likely valid, the
%% infrastructure invokes the oracle to check correctness.

@@

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
%\begin{wraptable}[20]{t}[0pt]{0.5\textwidth}

\begin{table*}
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

The workflow described in Section~\ref{sec:design} is currently
functional. This section shows preliminary results obtained with our
infrastructure providing some evidence that finding bugs in JS runtime
engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42 days. For example, bug \# 6 was manifested by the JS code \CodeIn{var
  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
function that returns a primitive value identifying the target
object~\cite{valueof}. That function returns an empty string in the
original version of this code. The modified version of the code
returns a string representation of a null character (called
\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
is equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
that converts a string to a number, otherwise the operation returns NaN 
(Not a Number)\cite{unary-plus}. For this case, Chakra evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.

So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any new bug on SpiderMonkey and V8; the bugs we
found were duplicates and were not reported. Finally, it is
worth noting that 7 of the 17 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

%\section*{Acknowledgment}

%\bibliographystyle{IEEEtran}
\bibliographystyle{plain}
\bibliography{references,../docs/google-research-awards-latam/tmp}

@@
